---
title: "Coursera: Developing Data Products Course Project"
author: "Gilbert Duerme"
date: "August 16, 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## A. Overview

This course project was made in fulfillment of the course requirements in the Developing Data Products course under Coursera. The course assignment was to Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using the created application.

## B. Shiny Application 

The shiny application done was a simple temperature converter in which the user can choose any options on how the value that he entered could be converted. The following conversions were made for this project:

- Fahrenheit to Celsius
- Fahrenheit to Kelvin
- Celsius to Fahrenheit
- Celsius to Kelvin
- Kelvin to Fahrenheit
- Kelvin to Celsius

## C. Shiny: ui.R

```{r, echo = TRUE, warning = FALSE, message = FALSE, cache = TRUE}
library(shiny)
shinyUI(fluidPage(
  titlePanel("Temperature Converter"),
  sidebarLayout(
    sidebarPanel(
      fluidRow(
        fluidRow(
          
          column(12, 
                 textInput(inputId = 'temp', label = textOutput(''), 
                           value = "", placeholder = "Enter the value"))
        ),
        
        column(12,
               radioButtons(inputId = "option", label = "Options:", choices = list("Fahrenheit to Celsius" = 1, "Fahrenheit to Kelvin" = 2, "Celsius to Fahrenheit" = 3, "Celsius to Kelvin" = 4, "Kelvin to Fahrenheit" = 5, "Kelvin to Celsius" = 6)))
      ),
      
      actionButton("convert", label = "Convert")
    ),
    
    mainPanel(
      h2(textOutput("result"))
    )
  ))
)
```


## C. Shiny: server.R

```{r, echo = TRUE, warning = FALSE, message = FALSE, cache = TRUE}
library(shiny)

FahrenheitToCelsius <- function(Fahrenheit1) {
  ((Fahrenheit1 - 32) * 5) / 9
}

FahrenheitToKelvin <- function(Fahrenheit2) {
  (((Fahrenheit2 - 32) * 5) / 9) + 273.15
}

CelsiusToFahrenheit <- function(Celsius1) {
  ((Celsius1 * 9) / 5) + 32
}

CelsiusToKelvin <- function(Celsius2) {
  (Celsius2 + 273.15)
}

KelvinToFahrenheit <- function(Kelvin1) {
  (((Kelvin1 - 273.15) * 9) / 5) + 32
}

KelvinToCelsius <- function(Kelvin2) {
  (Kelvin2 - 273.15)
}

shinyServer(
  function(input, output) {

    
    result <- eventReactive(input$convert, {
      input$temperature
      temp <- as.numeric(input$temp)
      
      if(input$option == 1){
        fc <- FahrenheitToCelsius(temp)
        paste(fc, ' degree Fahrenheit')
      }
      
      else if (input$option == 2){
        fk <- FahrenheitToKelvin(temp)
        paste(fk, ' degree Kelvin')
      }
      
      else if (input$option == 3){
        cf <- CelsiusToFahrenheit(temp)
        paste(cf, ' degree Fahrenheit')
      }
      
      else if (input$option == 4){
        ck <- CelsiusToKelvin(temp)
        paste(ck, ' degree Kelvin')
      }
      
      else if (input$option == 5){
        kf <- KelvinToFahrenheit(temp)
        paste(kf, ' degree Fahrenheit')
      }
      
      else{
        kc <- KelvinToCelsius(temp)
        paste(kc, ' degree Celsius')
      }
    })
    
    output$result <- renderText({
      result()
    })
  }
)
```

## D. Actual link of the created shiny application

The created shiny applicaiton can be viewed using this link: <https://github.com/giduerme/Developing-Data-Products-Course-Project>

